Title

### 2024-08-29 paper.tex
delete some garbage

\section{The components of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
Recall from \cref{sn_iso} that 
\[S \times_\mathfrak{g} \widetilde{\mathcal{N}} \cong \{(A_{X,a,b}, (U_i), (V_i)) : \forall i. \; XU_{i + 1} \subseteq U_i; \forall i. \; A_{X,a,b} V_{i + 1} \subseteq V_i\}.\]
We defined \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) by \((A_{X,a,b}, (U_i), (V_i)) \mapsto X\), and called \(\pi^{-1}(X)\) the \(n\)-Slodowy-slice Springer fiber at \(X\).
\begin{theorem}\label{springer_fiber_comps}
    \(\pi^{-1}(J(\lambda)) \cong \mathcal{P}_{J(\lambda)} \times X_\lambda\).
    Each irreducible component of \(\pi^{-1}(J(\lambda))\) has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j) + \sum_{i \neq j} \min(\lambda_i, \lambda_j)\).
\end{theorem}
\begin{proof}
    The isomorphism sends \((A_{X,a,b}, (U_i), (V_i))\) to \(((A_{X, a, b}, U_i), (V_i))\).
    The irreducible components of \(\mathcal{P}_{J(\lambda)}\) are given by \cref{p_comps}.
    Those of \(X_\lambda\) are given by \cref{usual_springer_fiber}.
    Adding the dimensions gives the claimed result.
\end{proof}

Conjugating \(\pi^{-1}(J(\lambda))\) by \((centralizer of X) \times \{I_n\}\) gives \(m^2 - \sum_{ij} \min(\lambda_i,\lambda_j)\) extra dimensions.

the Springer fiber at the \(n\)-Slodowy slice at

Define \(R = \{(X, \mathfrak{b}_1, \mathfrak{b}_2) : X \in \mathfrak{b}_1 \land u(X) \in \mathfrak{b}_2\} \subseteq \mathcal{S}_{m,n}' \times \mathcal{B}_{m + n} \times \mathcal{B}_m\).
We can obtain a subvariety of \(R\) by requiring that \(u(X)\) is in some fixed similarity class.
We expect that each of these subvarieties is an irreducible component of dimension \(m^2\).
We will verify these things using our prvious computations of springer fibers.

>>>>

\section{The components of \texorpdfstring{\(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\)}{S x\_g N}}
Recall from \cref{sn_iso} that 
\[S \times_\mathfrak{g} \widetilde{\mathcal{N}} \cong \{(A_{X,a,b}, (U_i), (V_i)) : \forall i. \; XU_{i + 1} \subseteq U_i; \forall i. \; A_{X,a,b} V_{i + 1} \subseteq V_i\}.\]
We defined \(\pi : S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \mathcal{N}_m\) by \((A_{X,a,b}, (U_i), (V_i)) \mapsto X\), and called \(\pi^{-1}(X)\) the \(n\)-Slodowy-slice Springer fiber at \(X\).
\begin{theorem}\label{springer_fiber_comps}
    \(\pi^{-1}(J(\lambda)) \cong \mathcal{P}_{J(\lambda)} \times X_\lambda\).
    Each irreducible component of \(\pi^{-1}(J(\lambda))\) has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j) + \sum_{i \neq j} \min(\lambda_i, \lambda_j)\).
\end{theorem}
\begin{proof}
    The isomorphism sends \((A_{X,a,b}, (U_i), (V_i))\) to \(((A_{X, a, b}, U_i), (V_i))\).
    The irreducible components of \(\mathcal{P}_{J(\lambda)}\) are given by \cref{p_comps}.
    Those of \(X_\lambda\) are given by \cref{usual_springer_fiber}.
    Adding the dimensions gives the claimed result.
\end{proof}
Conjugating \(\pi^{-1}(J(\lambda))\) by \(\GL_m \times \{I_n\}\) gives \(m^2 - \sum_{ij} \min(\lambda_i,\lambda_j)\) extra dimensions.
